
This is to illustrate central limit theorem in rmarkdown using bootstrap. This is to perform using to random sample and 2 expoenetial sample and produce histogram for both original sample and bootstram sample to illustrate central limit theorem and also to upload the rmarkdown file to Github.

Central Limit Theorem (CLT) Say we take a SRS of size from any population with mean and standard deviation .
If is large enough, the sampling distribution of the sample mean is approximately normal with mean and standard deviation.

I am taking 2 sample normal randon sample of size 10 and 20 and exponential sample of size 10 and 20.

```{r BootStrap_exec}
##Two rnorm samples of differing sample sizes
smpl1 <- rnorm(10,0,10)  #first sample of size 10.
smpl2 <- rnorm(20,0,10)  #second sample of size 20.

##Two rexp samples of differing sample sizes
expnsmpl1 <- rexp(10)  #small sample size
expnsmpl2 <- rexp(20) #large sample size

##vector to hold the 1000 samples.

r <-1000
bootmeansmpl1 <- numeric(r)
bootmeansmpl2 <- numeric(r)
bootmeanexpn1 <- numeric(r)
bootmeanexpn2 <- numeric(r) 

##this is bootstrap for loop to thsat run 1000 sample for above define vectors.
# and to define means of 1000 samples of our original dataset.

for (i in 1:r) {
  bootsmpl1 <- sample(smpl1, size = length(smpl1), replace =T )
  bootsmpl2 <- sample(smpl2, size = length(smpl2), replace =T )
  bootexpn2 <- sample(expnsmpl2, size = length(expnsmpl2), replace =T )
  bootexpn1 <- sample(expnsmpl1, size = length(expnsmpl1), replace =T )
  bootmeansmpl1[i] <- mean(bootsmpl1)
  bootmeansmpl2[i] <- mean(bootsmpl2)
  bootmeanexpn1[i] <- mean(bootexpn1)
  bootmeanexpn2[i] <- mean(bootexpn2)
}

```

Now here we have produce histogram of original random normal sample of 10 and 20 samples. and boostrap sample for the mean of 1000 samples.

```{r rnormHist, echo = FALSE}
  par(mfrow=c(2,2))
  hist(smpl1, main = "Histogram of original sample")
  hist(bootmeansmpl1, main = "Histogram of boorstrap sample")
 
  hist(smpl2, main = "Histogram of original sample")
  hist(bootmeansmpl2, main = "Histogram of boorstrap sample")
```

Its very clear from the histogram that size of the histogram is sqewed but when we have increase the size of sample using bootstram the data becomes normally distributed.

```{r rexpHist, echo = FALSE}
par(mfrow=c(2,2))
  hist(expnsmpl1 , main = "Histogram of original exponential sample")
  hist(bootmeanexpn1, main = "Histogram of boorstrap exponential sample") 

  hist(expnsmpl2 , main = "Histogram of original exponential sample")
  hist(bootmeanexpn2, main = "Histogram of boorstrap exponential sample") 
```

You see clearly that the original dataset is skewed, but when randomly samples through a bootstrap mechanisms - the distribution of averages becomes normally distributed.

